---
title: "mentorship2"
author: "Abena Mantebea"
date: "10/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

Hello Abena, hope you are doing well? This is R Markdown. You are basically doing everything you did in your R script over here. You can see that you installed and loaded the packages used in the Rscript and included another; 'here'. You learnt about R chunks which can be located at the top right of this page (the green C button). You worked in these chunks. Ensure your cursor is not in a chunk when creating a new chunk. After installing the packages, you imported from your working directory, the folder 'data' and the file 'cancer_data.csv' and assigned it to the object 'mantebs'. You went further to input the skim and glimpse commands but you didn't run them. Such a beautiful work done here Abena. Thank you RD Eric Komla Anku. 

```{r}
# install and load packages
pacman::p_load (tidyverse,skimr,rio,here)
```


```{r}
mantebs<-import(here("data","cancer_data.csv"))
```


```{r}
#skim dataset
skim(mantebs)
```


```{r}
#glimpse dataset
glimpse(mantebs)

```

